---
title: "Homework 6"
author: "Ling Yi"
date: "11/24/2020"
output: github_document
---


```{r}
library(tidyverse)
library(modelr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 1


```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
  
```

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x=city_state, y = OR))+
  geom_point()+
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

From this graph, we see that New York, NY has the lowest OR and a narrow confidence interval while Albuquerque, NM has the highers OR and a fairly wide confidence interval. 

# Problem 2

Uploading the dataset, cleaning, and converting numerical varibles to factors if needed. These variables include babysex, frace, mrace, maform. There is no missing data. 

```{r}
child_df = 
  readr::read_csv("./data/birthweight.csv") %>%
  janitor::clean_names() %>%
    mutate(
    babysex = factor(babysex, labels = c("male", "female")),
    frace = factor(frace, levels = c(1, 2, 3, 4, 8, 9), labels = c("white", "black", "asian"," puerto_rican", "other", "unknown")),
   mrace = factor(mrace,  c(1, 2, 3, 4, 8, 9), labels = c("white", "black", "asian"," puerto rican", "other", "unknown")),
   malform = factor(malform, labels = c("absent", "present"))
     )

sum(is.na(child_df))
```

My proposed hypothesis states that factors affecting a baby's birth-weight includes gestational age in weeks, mother's age at delivery, mothers race, mother's pre-pregnancy BMI, and family income. 

```{r}
fit = lm(bwt~ gaweeks + mrace + momage + ppbmi + fincome, data = child_df)

```

Plotting the predictions and residuals for the above model. 

```{r}
child_df %>%
  add_residuals(fit) %>%
  add_predictions(fit) %>%
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()  + 
  geom_smooth(se = TRUE, color = "red") + 
  labs(title = "Predicted vs residuals", 
       x = "Predicted", 
       y = "Residuals")
```

Modeling length at birth and gestational age as predictors (main effects only)

```{r}
fit1 = lm(bwt~ blength + gaweeks, data = child_df)

broom::tidy(fit) %>% 
    knitr::kable()
```

Modeling head circumference, length, sex, and all interactions (including the three-way interactions) between these variables. 

```{r}
fit3 = lm(bwt~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex , data = child_df)
```

Cross validations with crossv_mc

```{r}
cv_child_df = 
  crossv_mc(child_df, 100) 

##make into a tibble

cv_child_df =
  cv_child_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

Cross-validating prediction accuracy of my model with the other two proposed in the homework. 

```{r}
cv_child_df =
  cv_child_df %>% 
  mutate(
    fit  = map(train, ~lm(bwt~ gaweeks + mrace + momage + ppbmi + fincome, data = .x)),
    fit1 = map(train, ~lm(bwt~ blength + gaweeks, data = .x)),
    fit2 = map(train, ~lm(bwt~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))
    ) %>%
      mutate(
        rmse_fit = map2_dbl(fit, test, ~rmse(model = .x, data = .y)),
        rmse_fit1 = map2_dbl(fit1, test, ~rmse(model = .x, data = .y)),
        rmse_fit2 = map2_dbl(fit2, test, ~rmse(model = .x, data = .y))
        )
```

```{r}
cv_child_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
Fit2 (the model with the interactions terms) is the best fit for these variables because it has the lowest root-mean-square deviation. 

# Problem 3

Getting the dataset

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Getting the r-squared for 5000 bootstap samples

```{r}
rsq_df =
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)) %>%
    select(-strap, -models) %>% 
      unnest(results) 
```

Graphing the results

```{r}

rsq_df %>% 
  ggplot(aes(x = r.squared)) + 
  geom_density() +
  labs(
    title = "Distribution of R-squared",
    x = "R-squared",
    y = "density"
  )

```
The 95% confidence interval of R-squared distribution is (`r round(quantile(pull(rsq_df, r.squared), probs = c(0.025,0.975)), digits = 2)`).

```{r}
log_df = 
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)) %>%
  select(-strap, -models) %>% 
  unnest(results) %>%
  select(.id, term, estimate) %>% 
   pivot_wider(
    names_from = term, 
    values_from = estimate) %>%
  rename(
    beta_0 = "(Intercept)") %>%
    mutate(
      logB = log(tmin*beta_0)
         ) 
```

 Plotting the results
 
```{r}
log_df %>%
  ggplot(aes(x = logB)) + 
  geom_density() +
  labs(
    title = "Distribution of log(beta0*beta1)", 
    x = "log(beta0*beta1)",
    y = "density"
  )
```
 The 95% confidence interval of the Log(beta0*beta1) distribution is (`r round(quantile(pull(log_df, logB), probs = c(0.025,0.975)), digits = 2)`).

